A Switching Planner for Combined Task and Observation Planning

### 2010-11-19 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
New abstract from Richard.
 -0 Charles

\pdfinfo{
/Title (Switching in Continual Planning for Practical Robot Control)
/Subject (Proceedings of the 21st International Conference on Automated Planning and Scheduling)
/Author (NA)}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%\title{Switching in Continual Planning for Practical Robot Control}
\title{A Continual Planner that Switches Between Serial and
  Decision-Theoretic Planning} 
\author{NA}
\setcounter{secnumdepth}{0}

@@

The problem of practical robot control poses many important challenges
to automated planning.

Planning and plan execution must be robust, seamlessly accommodating
exogenous events and the underlying unpredictability of the
environment.

Plans with a reasonable chance of exhibiting good behaviours must be
synthesised in a timely manner.

@@

>>>>

\pdfinfo{
/Title (Switching in Continual Planning for Practical Robot Control)
/Subject (Proceedings of the 21st International Conference on Automated Planning and Scheduling)
/Author (NA)}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%\title{Switching in Continual Planning for Practical Robot Control}
\title{A Switching Planner for Combined Task and Observation Planning}
%\title{A Continual Planner that Switches Between Serial and
%  Decision-Theoretic Planning} 
\author{NA}
\setcounter{secnumdepth}{0}

@@

Realistic robot planning problems in uncertain environments often
require achieving tasks while also finding out about the
world. Because the world state cannot be observed directly, these
problems are naturally represented as partially observable Markov
decision problems (POMDPs). However, these are typically intractable
for realistic problems.

We present a \emph{switching planner} that employs fast sequential
planning to decide on the overall strategy, and uses a
decision-theoretic planner to solve the subproblems where partial
observability will significantly impact the quality of the plan. We
demonstrate the approach in a realistic robot exploration domain.

@@

From an automated planning perspective, the problem of practical
mobile robot control poses important and contrary challenges.
%%
On the one hand, planning and execution monitoring must be
lightweight, robust, timely, and should span the lifetime of the
robot. Those processes must seamlessly accommodate exogenous events,
changing objectives, and the underlying unpredictability of the
environment.
%%
On the other hand, robot planning should perform computationally
expensive reasoning about contingencies, and possible revisions of
subjective belief according to quantitatively modelled uncertainty in
acting and sensing.

In this paper we address these challenges, developing a continual
planner that switches between sequential and decision-theoretic
planning. Given a POMDP model of the environment, serial planning is
responsible for an initial deterministic sequential plan and
complementary runtime evolution of the decision process. That plan is
executed until an assumption about a runtime proposition

posted by a motivational component of the underlying robotic
architecture.

contingent sensory plans that are tailored to current
objectives.

In this paper we present an approach to continual planing that uses
two planning systems. The first

 to a distinct class of
challenges. We suppose 
%%
The underlying environment is modelled as a POMDP. We use the fast
classical satisficing system FastDownward to find a deterministic
sequential plan and complementary runtime evolution of that
process. This corresponds to a generalisation of replanning in
probabilistic planning to problems with partial observability.

Interaction between the serial planner and execution proceeds
more-or-less analogously to popular replanning approaches

Addressing these challenges in a monolithic framework, we present a
{\em switching} continual planner, that uses the fast serial
satisficing procedure FastDownward to perform net-benefit
%%
makes reasonable assumptions about the evolution of the runtime state
given a POMDP model of the environment.

contingent sensory plans that are tailored to current
objectives.

The decision-theoretic planner is able to tailor sensory processing on
a robot platform to the current objective, while FastDownward  quickly

In this paper we develop a continual planing system that uses two
planning systems. The first, is a state-of-the-art domain independent
planner for deterministic problems. The second is a information-state
contingency planning the information-state space of

Continual planning is a powerful technique that goes some way to
addressing those challenges. That approach interleaves planning and
execution, deliberately postponing planing for contingencies unless
they eventuate during execution.

computing a single serial plan and
eventuality

To these challenges it seems a continual planning approach is best,

where the runtime state evolves during plan execution

the latter is able to tailor sensory processing on a robot platform,
in order that it.

{\em ad-hoc}

probabilistic sequential decision making in practical sized problems
is intractable.

quantitative probabilistic models of the perception and action .
